\Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-13 articles/2014/whisper/aricleEbauche/articleIrodsUserMeeting.tex
Finished draft of it results

	\begin{enumerate}
  	  \item Whisper: an opportinuty to test and try to improve IT Infra for the data-intensive case
  	  \item Other project which permits also some advanced? Or "In genral each scientific case brings its own needs of new specification, functionality.
	  \item Add new functionality with cigri V3: more control for the user (max job, env variable, customize cluster)
	  \item Intro Irods: Data-intensive processing adress specific questions for Irods compare to files system
	  \item i-commands encapsulating to deal with timeouts and connection control (secure\_iget)
	  \item Specific rules for specific Irods server (dedicated data)?
	  \item Specific policies to acces files?
      \item Irods server overload with a lot of small file tranfers (schema client/irods server/icat)
      \item Network overload with automatic staging
      \item Finish: Despite the problems, this allows processing of terabytes of data within hours.
	\end{enumerate}

@@

  \item Network overload with automatic staging
  \item Using pyrods

@@

>>>>

@@

  \item We issued some network overloads: automatic staging, as set up for a site that has a lower bandwidth than the others may result in a lot of background irods processes doing the replication even when connection rate limit is set up on the servers and even when iget commands are aborted. Under some circumstances, it may completely overload a 1Gb/s ethernet link between 2 sites. Another overload encountered was when the user activates the -Q (use RBUDP (datagram) protocol for the data transfer) option. Even from a single node, this option can cause dramatic overload of network interfaces. Maybe iRODS should implement better rate limit control. 
  \item We made some preliminary tests of the python bindings of the iRODS API (called Pyrods). We noticed that when you have a lot of small operations to do from a python code (like in the Whisper project), either creating a lot of small files, or meta-data, Pyrods may be 10 times faster than a shell loop with i-commands inside. We are now making code examples for the other users to be able to take benefits from this method that would have been useful for the Whisper project.

@@

Despite the problems that have been solved or not, we are currently able to process terabytes of data within a few hours, and product good scientific results in a reduced delay, therefore we may say that Whisper+CiGri+iRODS is a great success!
